---
title: "Assignment 2"
subtitle: "STATS 220 Semester One 2022"
author: "Peter Cory"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

<!--
NOTE: You need to re-use at least two techniques you learned from Assignment 1 about working with R Markdown to create HTML, in addition to what is specified below.
-->

## Introduction
<!--
Explain what aspect(s) of music listening preferences/habits decided to focus on for your report.
Write at least 50 words.
-->


## Links to form and data
Here are the links to my Google form and the CSV file.

link to the Google form: [here](https://forms.gle/M8Y4VV26MJEnSJt58).

link to the CSV file: [here](https://docs.google.com/spreadsheets/d/e/2PACX-1vRxp5enJaTk_6ku44RVKr4knFQfLHR9lDOahJqpknig2wlRg527YCZyMrd0_tkwawBdGEN0lTLQhA-N/pub?output=csv).

## Analytics
<!--
Read the data from your published CSV file into a data frame called music_data. - Done

Rename the variables of your data frame and print five rows of your data using slice() and knitr::kable(). - Done

Include two examples of using inline R code to apply functions to your data frame or variables (extracted as vectors). - Done

Include at least three bar charts produced using {ggplot2} with appropriate labels.

Provide some comments that discuss what you have learned from your data.
-->
```{r warning = FALSE}
music_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRxp5enJaTk_6ku44RVKr4knFQfLHR9lDOahJqpknig2wlRg527YCZyMrd0_tkwawBdGEN0lTLQhA-N/pub?output=csv") %>% data.frame()

music_data <- music_data %>%
  rename(stream_srv = 2, music_or_podcast = 3, podcast_type = 4, music_type = 5, weekly_hours = 6, weekly_tracks = 7)
knitr::kable(slice(music_data,1:5))

responders <- length(music_data$Timestamp)

music_listeners <- sum(str_count(music_data$music_or_podcast,"Music"))

podcast_listeners <- sum(str_count(music_data$music_or_podcast,"Podcasts"))


```

Of the `r responders` people who have responded to the survey so far `r music_listeners` of them listen to music, that's `r music_listeners/responders*100`% of them! In total they have listened to `r sum(music_data$weekly_hours)` hours of music or podcasts in a week, that's a staggering `r round(sum(music_data$weekly_hours)/24, digits = 1)` days worth of non-stop listening!


## Learning reflection
<!--
Describe in your own words at least ONE important idea you learned from Module 2 Creating dynamic reporting systems.

Explain how you have re-used two techniques you learned from Assignment 1 (these can’t be things specifically asked for in this assignment).

Discuss what things related to data technologies that you are more curious about exploring further.

Write at least 150 words for this section of your report.
-->

### ONE important idea I learned from Module 2 Creating dynamic reporting systems.

I can see some interesting uses for an automatically updating website based on the data received, and R is an easy way of reading that information in and creating an understandable graphic.

### two techniques I reused from Assignment 1.

image_append() and dancing script for 3 and 4 titles

### What things related to data technologies am I curious about exploring further.

Last year I wrote a program which automatically plays an online HTML game called Cookie Clicker. I think it could be fun to take the information that the program collects, in order to play the game, and use it to create a webpage that shows the stats from the game - such as golden cookies clicked or total cookies made. (I have added to my github repo from Assignment 1 if you are interested).


