---
title: "index"
author: "Peter Cory"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(jsonlite)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = TRUE}
# Colours: #716867 Grayish, #db6965 Reddish, #82cdf0 Sky blue, #edc262 Yellow gold, White
Pokemons <- fromJSON("Spotify.json")

measurables <- Pokemons %>%
  select(danceability, energy, key_name, loudness, mode_name, speechiness, acousticness, instrumentalness, liveness, valence, tempo, time_signature, duration_ms)
dance_df <- data.frame(
  dance = c("Waltz","Vienese Waltz","Foxtrot","Quickstep","Tango","Cha Cha Cha","Rumba","Samba","Jive","Paso Doble","Lindy Hop","Charleston","Balboa","Jitterbug","Blues","Tango Argentino","Tango Nuevo","Milonga","Vals","Salsa","Merenge","Bachata"),
  min_tempo = c(84,174,112,200,120,120,100,96,168,120,105,200,175,120,20,80,40,150,150,180,130,90),
  max_tempo = c(90,180,120,208,140,128,108,104,184,124,190,290,340,250,75,160,160,240,240,300,200,200)
)

keys_name <- c("A","A#","B","C","C#","D","D#","E","F","F#","G","G#")
keys_num <- c(9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7, 8)

measurables <- measurables %>% mutate(
  key_num = keys_num[match(key_name, keys_name)])

measurables <- measurables %>%
  select(energy, liveness, valence, tempo, time_signature, key_num)


```


```{r}
#ggplot(measurables, aes(tempo, time_signature))+
#  geom_point()
#ggplot(measurables, aes(key_num, time_signature))+
#  geom_point()
#ggplot(measurables, aes(tempo, valence))+
#  geom_point()

#create own function last week lab to return ggplot

plot_graph <- function(data_frame, something_1, something_2){
  ggplot(data_frame, aes(something_1, something_2))+
    geom_hex()
}

plot_graph(measurables,measurables$tempo,measurables$valence)

```


## Why I chose this story.

I have very eclectic tastes, and like a lot of different things. Two of these are the Pokemon series and dancing, and I wanted to combine these into something different and interesting for this assignment.

## why I decided to focus on certain variables.

I decided to focus on the time signature, key and tempo variables as these are variables that can change depending on the different types of dance you are doing. I wanted to compare these three main variables with each other as well as some of the other numeric values to see if there is any correlation and then see which type of dance they would be ebst suited for.

  

## Why I chose the chart type(s) used.

I got the idea for the scatter plots from [here] which I used to see if there was any correlation between the variables I had chosen.

  

## How I applied the “grammar of graphics”


  
## Things I tried that didn’t work.

A couple of outliers a 1/4 time and a 5/4 time which are possible but 1/4 time is very rare and usually only for a beat. (also) outliers in the tempo (there was a 200bpm song which was not that fast) Unfortunately it is very difficult to double check these numbers as any other sites that offer the same services pull most of their data from Spotify, or are in some way associated with them.

  
## Overall conclusion.

In conclusion this assignment ended up being more a delve down a rabbit hole